TODO

### 2022-12-07 write-ups/cogsci23_paper/manuscript.Rmd
start results text

TODO introduction

@@

@@

## Reduction of referring expressions

@@

>>>>

# introduction

@@

We extracted a total of ZZ referring expressions,

@@

We assess the list of key points given at the beginning.

## Reduction of referring expressions
First thing to check is the key phenomena that over the course of iterated references, the referring expressions get shorter. We see that in Fig ??. Across both conditions, the number of referring words per trial/game decreases, which is driven by a decrease in the length of each referring expression. The number of referring expressions remains constant (although shows a group difference).

On average, in each trial, ZZ distinct flowers were referred to (this stayed relatively constant) with most trials having 2 or 3 referred to ()
TODO! double check that this is handling 0s appropriately!!
Each player usualy referred to one, with a minority referring to 2 or 3. This is consistent with a strategy where players say which flower they are selecting; higher numbers probably involve more coordination and info sharing.

TODO include model!

@@

Many of the key reduction findings from tangrams generalize to this situation. Specifically, we see utterance reduction over time and w/i group convergence for each image and divergence between images. This situation is different in that we have different stimuli (more natural) and the set up is collaborative and more free-form in what is talked about. These patterns hold for both the individual and group payoff structures.

One difference we see is that groups don’t diverge (from each other). This may be dependent on stimulus properities (are there universal features of some of the images?) and group dynamics

Conclusion: The key reference game findings have some generalizability. Settings like this one may be useful for encouraging discussion of a set of images and setting up partial knowledge situations.
